A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-06-09 results.tex
Update on Overleaf.
adding better regional png and species/sector table

In order to test the \code{aneris} harmonization procedure, results from the IAM
MESSAGE-GLOBIOM \cite{fricko_marker_2017} was processed. Two scenarios from the
SSP scenario library \cite{Riahi2017153,Rao2017346} are investigated. The SSP2,
or ``middle of the road'', scenario family is chosen to be analyzed because
MESSAGE-GLOBIOM is the marker scenario for this SSP. Of all SSP2 scenarios, the
reference (marker) and SSP2-45 scenarios are analyzed. Notably, emissions from
multiple sectors tend to increase in the reference scenario, thus testing the
harmonization mechanism with an increasing emissions pathway. The SSP2-45
scenario, where the ``45'' designation refers to a scenario with end-of-century
emissions resulting in approximately a 4.5 $\frac{\text{W}}{\text{m}^2}$
radiative forcing due to both warming from GHGs and fluoridated gases as well as
cooling from aerosols, is chosen because mitigation technologies and policies
are enacted causing a general reduction in pollutants and GHGs, including
(eventual) negative CO2 emissions in some regions and sectors due to carbon
capture and sequestration and afforestation. This scenario explores the
harmonization mechanism's response to generally decreasing emission
trajectories.

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs. Historical data is
taken from previously described LUC and anthropogenic sources, which comprise 10
separate pollutant and GHG species and 13 sectors. Therefore, a total of 1430
distinct trajectories were harmonized for each scenario.

@@

The harmonization of emissions pathways is performed in order to accurately
represent an updated historical emissions trajectory while also maintaining
consistency with the original, unharmonized pathway. As such, when the default
methods as provided by the harmonization procedure distort or otherwise
sufficiently misrepresent the underlying unharmonized results, an override
method is required to be provided for the trajectory of the region, sector, and
species in question. Based on the 2\% of total trajectories required to be
overridden, two classifications were observed: regional trajectories whose
\textit{magnitude} was overly distorted and regional trajectories whose
\textit{shape} was overly distorted.

>>>>

In order to test the \code{aneris} harmonization procedure, results from the IAM
MESSAGE-GLOBIOM \cite{fricko_marker_2017} was processed. Two scenarios from the
SSP scenario library \cite{Riahi2017153,Rao2017346} are investigated. The SSP2,
or ``middle of the road'', scenario family is chosen to be analyzed because
MESSAGE-GLOBIOM is the marker scenario for this SSP. Of all SSP2 scenarios, the
reference (marker) and SSP2-45 scenarios are analyzed. Notably, emissions from
multiple sectors tend to increase in the reference scenario, thus testing the
harmonization mechanism with an increasing emissions pathway. The SSP2-45
scenario, where the ``45'' designation refers to a scenario with end-of-century
emissions resulting in approximately a 4.5 $\frac{\text{W}}{\text{m}^2}$
radiative forcing due to both warming from GHGs and fluoridated gases as well as
cooling from aerosols, is chosen because mitigation technologies and policies
are enacted causing a general reduction in pollutants and GHGs, including
(eventual) negative CO2 emissions in some regions and sectors due to carbon
capture and sequestration and afforestation. This scenario explores the
harmonization mechanism's response to generally decreasing emission
trajectories.
% * <sfujimori112256@gmail.com> 2017-06-07T10:22:28.473Z:
% 
% As a supplementary, it would be better to show the total kyoto gases emissions for these two scenarios, which gives readers rough image what kind of scenarios we choose.
% 
% ^.

MESSAGE-GLOBIOM includes a representation of 11 distinct regions which can be
mapped directly to the 5-region definition used in the RCPs. Historical data is
taken from previously described LUC and anthropogenic sources, which comprise 10
separate pollutant and GHG species and 13 sectors shown in
\ref{tab:sp}. Therefore, a total of 1430 distinct trajectories were harmonized
for each scenario.

\begin{table}[]
  \centering
  \caption{Harmonized Species and Sectors}
  \label{tab:sp}
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Emissions Species}        & \textbf{Sectors}                    \\
    \hline
    Black Carbon (BC)                 & Agricultural Waste Burning          \\
    Hexafluoroethane (C2F6)           & Agriculture                         \\
    Tetrafluoromethane (CF4)          & Aircraft                            \\
    Methane (CH4)                     & Energy Sector                       \\
    Carbon Dioxide (CO2)              & Forest Burning                      \\
    Carbon Monoxide (CO)              & Grassland Burning                   \\
    Hydrofluorocarbons (HFCs)         & Industrial Sector                   \\
    Nitrous Oxide (N2O)               & International Shipping              \\
    Ammonia (NH3)                     & Residential Commercial Other        \\
    Nitrogen Oxides (NOx)             & Solvents Production and Application \\
    Organic Carbon (OC)               & Transportation Sector               \\
    Sulfur Hexafluoride (SF6)         & Unharmonized                        \\
    Sulfur Oxides (SOx)               & Waste                               \\
    Volatile Organic Compounds (VOCs) &
    \hline
  \end{tabular}
\end{table}

@@

The harmonization of emissions pathways is performed in order to accurately
represent an updated historical emissions trajectory while also maintaining
consistency with the original, unharmonized pathway. As such, when the default
methods as provided by the harmonization procedure distort or otherwise
sufficiently misrepresent the underlying unharmonized results, an override
method is required to be provided for the trajectory of the region, sector, and
species in question. Based on the 2\% of total trajectories required to be
overridden, two classifications were observed: regional trajectories whose
% * <sfujimori112256@gmail.com> 2017-06-07T10:28:41.326Z:
% 
% > regional trajectories whose
% > \textit{magnitude} was overly distorted and regional trajectories whose
% > \textit{shape} was overly distorted.
% 
% How can we detect these results?
% If we could have a systematic detection criteria, then it would be really worthwhile to describe.
% Otherwise, it means that the users of this tool generally  have to see all results by their eye, which could be essentially a weak point of this tool.
% If so, we may want to discuss that point in the discussion section,
% 
% ^.
\textit{magnitude} was overly distorted and regional trajectories whose
\textit{shape} was overly distorted.
